% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}

\begin{document}

\name{Emre YILDIZ - {\it Software Engineer}}
% \address used twice to have two lines of address
\address{emre.yildiz.dev@hotmail.com}
\address{\href{https://linkedin.com/in/emre-yildiz-297ab0242}{ Linkedin}} 


 
\begin{resume}
 
\section{SUMMARY}  As a dedicated and skilled software engineer with a strong foundation in functional programming and a passion for innovative technology solutions, I am seeking a challenging role in a forward-thinking company. My goal is to contribute my expertise in software development and my proficiency in modern programming languages to drive project success and technological advancement. I am particularly interested in opportunities that allow for continued learning and growth in areas such as cloud computing, AI, or other emerging technologies.
                
I planned my place in the IT world in a very broad framework. Because it is very enjoyable for me to research and develop everything related to technology.

I have a strong background in designing, implementing, maintaining web application, mobile application, blockchain dapps, and services, deploying and administration of applications  on the servers.

I developed .Net, Django, Flutter/Dart, Java, Swift UIKit, Angular, Typescript, Angular, Nextjs, AspNetBoilerplate projects for enterprise companies and set up their database Postgresql, back-end, MVC projects, and domains.
I want to work with companies that take software development really seriously.


\section{\textbf{ACCEPTED ROLES}} I definitely acknowledge my proficient skills based on the projects I have undertaken with various technologies. While my primary role is as a Software Engineer, I do not limit myself to this title. I have experience in the following roles:
\begin{itemize}
\item Backend Developer
\item Blockchain Dapps Developer
\item Mobile Developer
\item DevOps
\item Frontend Developer
\item Data Engineer
\item AI, Machine Learning Engineer
\end{itemize}

\section{\textbf{PROFICIENT SKILLS}} Although I have experience with a variety of programming languages, frameworks, and tools, I officially consider myself proficient in a technology when I have undertaken projects with it, such as:
\begin{itemize}
\item Dotnet, C\#, Entity Framework Core, MsSQL, Aspnet Boilerplate
\item NestJS, Microservices, Redis, MySQL, gRPC, RabbitMQ, Kafka
\item Angular, Typescript
\item NextJS
\item Flutter
\item React Native, Redux, React Query
\item Remix-run
\item Blockchain, Solidity, Javascript, Ethereum, ZkSync
\item Rust Axum, Leptos
\item Python, Django, FastAPI
\item Java, Spring Boot, Android
\item Swift, UiKit
\item Postgresql, MsSql, MySQL, Redis, CouchDB 
\item Git, Docker, Linux, Debian Linux, RedHat Enterprise Linux, Bash
\item Amazon Web Services (AWS)
\item Microservices, gRPC, RabbitMQ, Kafka, REST API, GraphQL
\item Agile, Scrum, Jira, Confluence, Trello, Wekan
\item Web Scrapping, Selenium
\item Nginx, HAProxy, Load Balancing, Cloudflare, S3 Storage, Minio, Coolify, Meilisearch
\end{itemize}

\section{\textbf{MODERATE SKILLS}}
\begin{itemize}
        \item Functional programming, Haskell, Scala, F\#, Elm, Purescript, Gleam
        \item Google Cloud, Azure
        \item Data Analysis, Numpy, Pandas, Octave, SageMath, Anaconda Data Science Platform
        \item Machine Learning, TensorFlow, PyTorch, Scikit-learn
        \item MongoDB, Cassandra, Elasticsearch
        \item CI/CD, Kubernetes
\end{itemize}
 
 
\section{EDUCATION}
                {\sl Master of Science,} \textbf{Computer Engineer} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Ege University 
                2024 - 2026 \\
                Concentration: Distrubuted Systems 

                {\sl Bachelor of Science,} \textbf{Computer Engineer} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Celal Bayar University 
                2020 - 2024 \\
                Concentration: Software Engineering \\
                Grade: 3.32 / 4.00 

                {\sl Bachelor of Science,} \textbf{Computer Engineer} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Ahmet Yassawi University 
                2019 - 2022 \\
                Concentration: Computer Science \\
                Grade: 3.81 / 4.00 
 
                {\sl Bachelor degree,} \textbf{Information Management Systems} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Anadolu University 
                2018 - 2021 \\
                Grade: 3.44 / 4.00 

                {\sl Associate's degree,} \textbf{Computer Programmer} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Dokuz Eylul University 
                2016 - 2018 \\
                Concentration: Computer Programming \\
                Grade: 3.40 / 4.00 
 
                {\sl Associate's degree,} \textbf{Mechatronics} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Sakarya University 
                2020 - 2022 \\
                Grade: 3.47 / 4.00 

                {\sl Bachelor's degree,} \textbf{Civil Engineer} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Celal Bayar University 
                1999 - 2003 \\
                
\newpage

\section{COMPUTER \\ SKILLS} {\sl Languages \& Tools:} \\
                \subsection{Web Development}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                   \item \textbf{C\#}, .NET Core, Abp Framework, MVC design, Entity Framework, Windows Forms, F\#
                   \item \textbf{Typescript\#}, Nextjs, Reactjs, Angular, Nestjs, Express
                   \item \textbf{Python}, Django, DjangoRestFramework, FastAPI, Flask, Shell scripting
                   \item \textbf{Java}, Spring Framework, Spring Boot, JavaFX Desktop Programming, Android Programming
                   \item \textbf{Rust}, Axum, Leptos
                 \end{itemize}
                 \subsection{Mobile Development}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                   \item \textbf{Android \& IOS Development}, Flutter, React Native, Android Java Programming
                   \item \textbf{Swift} IOS UIKit
                 \end{itemize}
                 \subsection{Blockchain Development}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                        \item Solidity, Hardhat, Foundry, Web3, Solana, Ethereum, ZkSync, Aptos, Move, Sui, Arbitrum
                        \item Market Bot Management 
                 \end{itemize}
                 \subsection{DevOps \& Server Management}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                   \item \textbf{Linux}, Server Management, Bash scripting, System Administration, Debian, Ubuntu, Fedora, Red Hat Enterprise Linux, Arch Linux, Clonezilla, Vim, Gnu/Emacs
                   \item \textbf{Git} Version Control Systems, Github, Gitlab
                   \item \textbf{Docker Containerization}, Virtualization, Virtualbox, Vmware
                   \item \textbf{Nginx}, HAProxy, Load Balancing, Cloudflare, S3 Storage, Minio, Coolify, Meilisearch
                   \item \textbf{Nix} reproducible developer environments
                   \item \textbf{Postgresql}, Psql, Pgadmin4, Postgrest 
                   \item \textbf{MSSQL}, Sql Management System 
                 \end{itemize}
                 \subsection{Cloud Computing}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                   \item \textbf{Cloud Computing}, Aws, Google Cloud, Digital Ocean, Azure
                   \item \textbf{Development Tools}, Apache Http Server, Nginx 
                 \end{itemize}
                 \subsection{Others}
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                   \item \textbf{Functional Programming}, Scala, Haskell, F\# functional programming design and concepts 
                   \item \textbf{Data Analysis}, Numpy, Pandas, Octave, SageMath, Anaconda Data Science Platform 
                   \item \textbf{Agile Development},  Scrum, Agile Testing, Unit Testing, NUnit, Redmine, Jira, Confluence, Trello, Wekan
                   \item \textbf{Graphics Design, Media Applications}, Inkscape, Gimp, Diagrams.net, Dia, Obs Studio, HandBrake, Kdenlive, Audacity, Wordpress
                 \end{itemize}
 
\section{EXPERIENCE} {\sl Software Engineer} \hfill  2017 - Present \\
                 \begin{itemize}  \itemsep -2pt % reduce space between items
               
               \item \textbf{ Blockchain Analysis, Education, News, Blogs Application:  } Developed web and mobile app with microservice backend as a Team Lead. (jrkripto.com)
                \begin{itemize}
                        \item NextJS frontend, React Native Mobile with Typescript
                        \item NestJS microservices backend with gRPC
                \end{itemize}
               \item \textbf{B2B e-commerce: } Developed an enterprise Angular frontend / Abp Dotnet Backend B2B app. (Altinyildiz Classics \& Beymen Business) 
                         \begin{itemize}
                                         \item \textbf{Angular: } Designed and developed enterprise Angular frontend.
                                         \item \textbf{Abp Dotnet: } Backend with Abp Dotnet 6.0.
                                         \item \textbf{Integration} Integrated with B2C app of the company. Product sync with B2C app, cronjobs, etc.
                         \end{itemize}
                 \item \textbf{Swift IOS: } Supported enterprise level Ipad app with Swift for new development features. (Organic clothing company)
                         \begin{itemize}
                                         \item Custom keyboard implementation for ordering product variants.
                                         \item new features of the company requirements.
                         \end{itemize}
                 \item \textbf{Flutter Mobile App: } Developed an enterprise Flutter mobile app for customer-welder portal. App launched on PlayStore and AppleStore.(Magmaweld / Zaimoglu Holdings) 
                         \begin{itemize}
                                         \item Dotnet 5.0 backend implementation and deployment to a Windows server
                                         \item Flutter IOS and Android implementation and deploy to PlayStore and AppleStore
                         \end{itemize}
                 \item \textbf{NFC Payment Mobile App: } Developed an enterprise Java mobile app for payment with NFC and bank gateway backend.(Altinyildiz Classics \& Beymen Business) 
                 \item \textbf{Enterprise Workflow Web Application: } Support an enterprise company workflow project for new developments and support. In this application 65.000 flow executed for various companies. (Yaşar Holdings / dijital.asistan software) 
                         \begin{itemize}
                                         \item Added REST API to the system for starting and managing workflows.
                                         \item Organize the whole version system with git.
                                         \item Implemented new features and bugfixes.
                         \end{itemize}
                \item \textbf{Blockchain Web Application: } web3 application.
                \begin{itemize} 
                                \item Nextjs frontend, Nestjs \& Mysql backend.
                                \item Token transactions and Bot management of the Blockchain markets.
                \end{itemize}
                \item \textbf{NestJS Backend Boilerplate : } Developed a NestJS backend boilerplate with Authentication, Authorization, Redis Cache, Bull Queue system, JWT, Cron Jobs, etc. 
                \item \textbf{BergX Software 2023-2024: } worked as a Tech Lead.
                \item \textbf{Gunkom Software 2021-2023: } worked as a Software Engineer. Developed various frontend and backend projects at enterprise level. 
                         \begin{itemize}
                                         \item Upgraded company core boilerplate framework to .NET Core 6.0
                                         \item Added Automation with python to core boilerplate development environment.
                         \end{itemize}
                 \item \textbf{Web Scrapping Data Analysis Web Application: } Developed a web application for representation with data analysis of on-sale devices that are web scrapped from various e-commerce websites. 
                 \item \textbf{Chess Course Management System: } Developed a web application to a chess club for student progress tracking, attendance, chess puzzle homework submission and grading software with C\#, .Net Core web framework and MSSql database. 
                \item \textbf{Web Applications: } Developed various small scaled web applications.
                \item \textbf{University Projects: } I explained many of the projects I carried out in detail in the Projects section.
                \end{itemize}
 
                {\sl  Instructor} \hfill             2017 - Present \\
                Betul Cemre YILDIZ Chess and Robotic Organization
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Teaching Csharp programming courses to high school students.
                 \item Performing  Linux Administration courses to high school students.
                 \item Giving Drone certificate courses.
                 \end{itemize} 

                 
                {\sl Company Manager} \hfill        2005 - 2015 \\
                Adacelik Engineering LLC
                  \begin{itemize}
                   \item We have done construction works in the public and private sector with my chief engineer duty.
                     
                   \item We produced furniture with 20 employees in the company I own.
                   \end{itemize} 

\section{University Projects}{\sl Celal Bayar University} \hfill        2020 - 2022 \\
                  \begin{itemize}
                   \item \textbf{Artificial Intelligence Project: } N-Queens problem solved with artificial intelligence algorithms and python programming language. 
                   \item \textbf{Tcp/Ip Network Programming Project: } Developed Battleship like multiplayer game with C\#, Windows Forms. Two clients can play and communicate each other in the same network. \href{https://github.com/emre-yildiz-dev/CinsFlagsGame}{https://github.com/emre-yildiz-dev/CinsFlagsGame}
                   \item \textbf{Twitter Clone Project: } Developed a basic twitter clone with .NET Core, C\#, EntityFramework Core and Postgresql
                    \item \textbf{ZeroToHundred Console Game: } Developed a Java console game that two sphere racing on a platform of numbers 1 to 100 in a Linux terminal emulator. \href{https://github.com/emre-yildiz-dev/zerotohundred}{https://github.com/emre-yildiz-dev/zerotohundred} 
                     \item \textbf{BASE Programming Language Design Project: } Developed a single programming language with python interpreter. \href{https://github.com/emre-yildiz-dev/BASE}{https://github.com/emre-yildiz-dev/BASE}
                     \item \textbf{E-commerce Back-end Programming Project: } Backend system with Java, Spring Boot REST Framework and Postgresql database.
                      
                    \end{itemize}
                  {\sl Akhmet Yassawi University} \hfill             2019 - 2022 \\
                  \begin{itemize}
                    \item \textbf{Fitness Center Web Application Project: } Developed Fitness gym promotion and membership purchase web application with Django framework, python, Sqlite database. \href {https://github.com/emre-yildiz-dev/Django-Fitness}{https://github.com/emre-yildiz-dev/Django-Fitness}
                     \item \textbf{Scientific Calculator Mobile Application Project: } Developed a mobile application that has scientific calculation properties with Intellij idea, Java, Android Sdk.
                     \item \textbf{Course Management System: } Developed .Net Core 6.0 web application with MSSql database.
                  \end{itemize} 
                  {\sl Dokuz Eylul University} \hfill             2017 - 2019 \\
                  \begin{itemize}
                    \item \textbf{C lang Console Program: } Developed a console program to save newly learned words for a foreign language. Then retrieve them from a file randomly to memorize activities. \\ \href{https://github.com/emre-yildiz-dev/ForeignWordMemorization}{https://github.com/emre-yildiz-dev/ForeignWordMemorization}
                  \end{itemize}
 
\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
                \textbf{FIDE Chess Trainer (FT)} fourth level expert trainer and tournament player \\
                \textbf{FMJD International Draughts Player} \\
                \textbf{Special Interest to Board Games} Checkers, Go, Xiangqi\\
                

\section{CONTACT}  \textbf{Email: } emre.yildiz.dev@hotmail.com \\ 
\textbf {Tel: } +90 532 563 0256 \\ 
\textbf {Linkedin: } \href{https://linkedin.com/in/emre-yildiz-297ab0242}{https://linkedin.com/in/emre-yildiz-297ab0242} \\ 
\textbf {Github: } \href{https://github.com/emre-yildiz-dev}{https://github.com/emre-yildiz-dev}\\ 
\textbf {Location: } Izmir/Turkey \\ 



\end{resume}
                 
\end{document}







